# Results 

## Catches on land {-}

### Purse seine and baitboat geo-referenced catch data set by month and 1°x1° grid area

Some of the geo-referenced catches available from IATTC, ICCAT, and IOTC are located on land (**Table \@ref(tab:MislocationLandCAPSBB11MTable)** and **Fig. \@ref(fig:barplot)**).


```{r tab.cap = "Summary of total catch from the purse seine and baitboat geo-referenced catch data set by month and 1°x1° grid area that are associated with grid squares located on land", tab.id = "MislocationLandCAPSBB11MTable"}
CA_PS_BB_11M_ON_LAND_RFMO_UNIT_FT = 
  CA_PS_BB_11M_ON_LAND_RFMO_UNIT %>%
  flextable() %>%
  flextable::font(fontname = "calibri", part = c("all")) %>% 
  align(part = "header", align = "center") %>% 
  colformat_double(digits = 0) %>%
  fontsize(size = 9) %>% 
  border_inner() %>% 
  border_outer(border = fp_border(width = 2)) %>% 
  merge_v(j = "RFMO") %>% 
  autofit() %>% 
  fix_border_issues()

CA_PS_BB_11M_ON_LAND_RFMO_UNIT_FT
```

```{r MislocationLandCA_PS_BB_11MMap, fig.cap = "Distribution of catches from the geo-referenced catch data set by month and 1°x1° grid area. (a) catches reported in metric tonnes; (b) catches reported in numbers of fish", fig.id = "barplot"}
include_graphics(paste0(here(),"/outputs/charts/mislocation/CA_PS_BB_11M_ON_LAND_MAP.png"))
```

### Geo-referenced catch data set by month and 5°x5° grid area

```{r tab.cap = "Summary of total catch from the geo-referenced catch data set by month that are associated with grid squares located on land", tab.id = "MislocationLandCA55MTable"}
CA_55M_ON_LAND_RFMO_UNIT_FT = 
  CA_55M_ON_LAND_RFMO_UNIT %>%
  flextable() %>%
  flextable::font(fontname = "calibri", part = c("all")) %>% 
  align(part = "header", align = "center") %>% 
  colformat_double(digits = 0) %>%
  fontsize(size = 9) %>% 
  border_inner() %>% 
  border_outer(border = fp_border(width = 2)) %>% 
  merge_v(j = "RFMO") %>% 
  autofit() %>% 
  fix_border_issues()

CA_55M_ON_LAND_RFMO_UNIT_FT
```

```{r MislocationLandCA_55MMap, fig.cap = "Distribution of catches from the geo-referenced catch data set by month and 5°x5° grid area. (a) catches reported in metric tonnes; (b) catches reported in numbers of fish", fig.id = "barplot"}
include_graphics(paste0(here(),"/outputs/charts/mislocation/CA_55M_ON_LAND_MAP_PAC.png"))
```


### Geo-referenced catch data set by time series

#### Geo-referenced catch data set by month 

```{r timeseriesmislocated, fig.cap = "Time series of catches from the geo-referenced catch data located on land set by month", fig.id = "timeseriesmislocated"}
include_graphics(paste0(here(),"/outputs/charts/mislocation/time_series_mislocated.png"))
```


```{r timeseriesmislocatedbytrfmos, fig.cap = "Time series of catches from the geo-referenced catch data located on land set by month and tRFMOs", fig.id = "timeseriesmislocatedbytrfmos"}

include_graphics(paste0(here(),"/outputs/charts/mislocation/time_series_mislocated_by_trfmo.png"))

```

The data located on land is higher for last decade, for every tRFMO and for each unit.

### Repartition of factors for data on land

```{r}

list_files <- as.list(list.files(here("outputs/charts/mislocation/pie_plot_factors")))

list_names <- as.list(toupper( gsub("_","",gsub("_repartition_pie_plot.png","",list_files))))

```



```{r}
resume_knit_child = function(x){

  knitr::knit_child(text = c(
    '',
    '```{r}',
    'name <- toupper( gsub("_","",gsub("_repartition_pie_plot.png","",x)))',
    '',
    '```',
    '',
    '',
    '',
    '',
    '',
    '',
    '```{r results = "asis", fig.cap = paste0("Distribution in value for the dimension : ",name)}',
    'include_graphics(paste0(here("outputs/charts/mislocation/pie_plot_factors/", x)))',
    '',
    '',
    '```',
    '',
    '',
    ''




  ), envir = environment(), quiet= TRUE)
}


```

```{r results='asis'}

t <- lapply(list_files, resume_knit_child)

```

```{r results='asis'}

cat(unlist(t), sep ="\\clearpage")

```


## Catches outside juridiction zone {-}

### Catches outside every juridiction zone


```{r CA_WITH_NO_COMPETENCE_AREA, fig.cap = "Reported captures on CWP grids being in none of the 4 competence areas", fig.id = "CA_WITH_NO_COMPETENCE_AREA"}

include_graphics(paste0(here(),"/outputs/charts/mislocation/CA_WITH_NO_COMPETENCE_AREA_MAP.png"))

```




```{r tab.cap = "Summary of total catch from the geo-referenced catch data set by month and 5°x5° grid area that are associated with grid squares located outside of the 4 competences areas", tab.id = "SUM_ALL_GRIDS_WIHOUT_COMPETENCE_AREA_SUMMARY"}

library(readxl)
SUM_ALL_GRIDS_WIHOUT_COMPETENCE_AREA_SUMMARY <- read_excel(here("outputs/datasets/SUM_ALL_GRIDS_WIHOUT_COMPETENCE_AREA_SUMMARY.xlsx"))

total <- sum(SUM_ALL_GRIDS_WIHOUT_COMPETENCE_AREA_SUMMARY$value)
species <- unique(SUM_ALL_GRIDS_WIHOUT_COMPETENCE_AREA_SUMMARY$species)

SUM_ALL_GRIDS_WIHOUT_COMPETENCE_AREA_SUMMARY = 
  SUM_ALL_GRIDS_WIHOUT_COMPETENCE_AREA_SUMMARY %>%rename(RFMO = source_authority) %>% 
  flextable() %>%
  flextable::font(fontname = "calibri", part = c("all")) %>% 
  align(part = "header", align = "center") %>% 
  colformat_double(digits = 0) %>%
  fontsize(size = 9) %>% 
  border_inner() %>% 
  border_outer(border = fp_border(width = 2)) %>% 
  merge_v(j = "RFMO") %>% 
  autofit() %>% 
  fix_border_issues()

SUM_ALL_GRIDS_WIHOUT_COMPETENCE_AREA_SUMMARY
```

This does not concern a lot of data and most of the cwp grid are only a bit outside a juridiction zone (i.e `r total` tons.) This however concern `r length(species)` species, which are `r species`. This include major tuna species.

## Catches outside declarant juridiction zone

```{r}
CA_OUTSIDE_COMPETENCE_AREA <- read_excel(here("outputs/datasets/CA_OUTSIDE_COMPETENCE_AREA.xlsx"))
```


```{r tab.cap = "Summary of total catch from the geo-referenced catch data that are associated with grid squares located outside of the competences area of the declarant", tab.id = "CA_OUTSIDE_COMPETENCE_AREA"}


CA_OUTSIDE_COMPETENCE_AREA_DF = 
  CA_OUTSIDE_COMPETENCE_AREA %>%distinct() %>% rename(RFMO = source_authority) %>% group_by(RFMO, unit)%>%arrange(RFMO, unit) %>%  
  flextable() %>%
  flextable::font(fontname = "calibri", part = c("all")) %>% 
  align(part = "header", align = "center") %>% 
  colformat_double(digits = 0) %>%
  fontsize(size = 9) %>% 
  border_inner() %>% 
  border_outer(border = fp_border(width = 2)) %>% 
  merge_v(j = c("RFMO", "unit")) %>% 
  autofit() %>% 
  fix_border_issues()

CA_OUTSIDE_COMPETENCE_AREA_DF
```

This concerns a few square for `r unique(CA_OUTSIDE_COMPETENCE_AREA$source_authority)`. 

```{r CA_OUTSIDE_COMPETENCE_AREA_OF_DECLARANT_MAP, fig.cap = "Reported captures on CWP grids being outside the competence zone of the declarant", fig.id = "CA_OUTSIDE_COMPETENCE_AREA_OF_DECLARANT_MAP"}

include_graphics(paste0(here(),"/outputs/charts/mislocation/CA_OUTSIDE_COMPETENCE_AREA_OF_DECLARANT_MAP.png"))

```


This mostly concern the IATTC / ICCAT zone close to the border.

