---
title: "Overlapping IOTC _ WCPFC"
date: '2023-05-16'
---

```{r include = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      fig.cap = TRUE, 
                      tab.cap.style = "Table Caption", 
                      tab.cap.pre = "Tab. ",
                      tab.cap.sep = ". ", 
                      fig.cap.style = "Image Caption", 
                      fig.cap.pre = "Fig. ", 
                      fig.cap.sep = ". ", 
                      warning = FALSE
                      )
```



```{r tab.cap = "Summary of total catch reported in the overlapping area between IOTC and WCPFC groupped by spatial resolution, unit and RFMO", tab.id = "CA_IN_OVERLAPPING_ZONES_IOTC_WCPFC_SUMMARY_GRIDTYPE"}

CA_IN_OVERLAPPING_ZONES_IOTC_WCPFC_SUMMARY_GRIDTYPE <- read_excel(here("outputs/datasets/CA_IN_OVERLAPPING_ZONES_IOTC_WCPFC_SUMMARY_GRIDTYPE.xlsx"))


CA_IN_OVERLAPPING_ZONES_IOTC_WCPFC_SUMMARY_GRIDTYPE_FLEXTABLE = 
  CA_IN_OVERLAPPING_ZONES_IOTC_WCPFC_SUMMARY_GRIDTYPE %>% rename(RFMO= source_authority)%>%
  flextable()  %>% 
  flextable::font(fontname = "calibri", part = c("all")) %>% 
  align(part = "header", align = "center") %>% 
  colformat_double(digits = 0) %>%
  fontsize(size = 9) %>% 
  border_inner() %>% 
  border_outer(border = fp_border(width = 2)) %>% 
  merge_v(j = c("GRIDTYPE")) %>% 
  autofit() %>% 
  fix_border_issues()

CA_IN_OVERLAPPING_ZONES_IOTC_WCPFC_SUMMARY_GRIDTYPE_FLEXTABLE
```


For the following document, we aggregate all the data being in 1 deg square in 5 deg as the data in 1 deg square cannot be compared, is coming only from IOTC and does not represent a huge percentage of the total catches reported in the overlapping area.

# Analysis of reported catches on the overlapping area

```{r tab.cap = "Summary of total catch reported in the overlapping area between IOTC and WCPFC groupped by species, unit and RFMO", tab.id = "CA_IN_OVERLAPPING_ZONES_IOTC_WCPFC_SUMMARY_SPECIES"}

CA_IN_OVERLAPPING_ZONES_IOTC_WCPFC_SUMMARY_SPECIES <- read_excel(here("outputs/datasets/CA_IN_OVERLAPPING_ZONES_IOTC_WCPFC_SUMMARY_SPECIES.xslx"))


CA_IN_OVERLAPPING_ZONES_IOTC_WCPFC_SUMMARY_SPECIES_FLEXTABLE = 
  CA_IN_OVERLAPPING_ZONES_IOTC_WCPFC_SUMMARY_SPECIES %>% rename(RFMO= source_authority)%>%
  flextable()  %>% 
  flextable::font(fontname = "calibri", part = c("all")) %>% 
  align(part = "header", align = "center") %>% 
  colformat_double(digits = 0) %>%
  fontsize(size = 9) %>% 
  border_inner() %>% 
  border_outer(border = fp_border(width = 2)) %>% 
  merge_v(j = c("species")) %>% 
  autofit() %>% 
  fix_border_issues()

CA_IN_OVERLAPPING_ZONES_IOTC_WCPFC_SUMMARY_SPECIES_FLEXTABLE
```

For most of the species, IOTC has bigger records of captures in number of fish and WCPFC in tons. However, for the major tunas, WCPFC has bigger records. 

Eventually, `r length(species_unique)` species have declaration only from one tRFMO in the overlapping zone. For those species : `r species_unique`, it seems to be better to keep all the data. Maps of the distribution for those species can be found in annexe.

For the remaining species, the data is not homogeniously overlapped.

## Doubled species 

```{r}
formals(list.files)$full.names <- TRUE
```


```{r}
resume_knit_child = function(x){
  knitr::knit_child(text = c(
    '',
    '```{r}',
    'name <- toupper(basename(gsub("single","",gsub("converted", "", gsub("and", "", gsub("charts","",gsub(".png","",gsub("doubledeclaration","",gsub("_","",gsub("plots","",x))))))))))',
    '',
    '```',
    '',
    '',
    '',
    '',
    '',
    '',
    '```{r results = "asis", fig.cap = paste0("Time series and maps of captures for the species : ",name)}',
    'include_graphics(paste0(x))',
    '',
    '',
    '```',
    '',
    '',
    ''




  ), envir = environment(), quiet= TRUE)
}


```


```{r include = FALSE}

list_files <- as.list(list.files(here("outputs/charts/overlapping/IOTC_WCPFC/species_doubled")))
list_charts_double_decla <- list_files[!str_detect(list_files,"converted")]
list_charts_double_decla <- list_files[str_detect(list_files,"single")]


```



```{r results='asis'}

t <- lapply(list_charts_double_decla,resume_knit_child)

```

```{r results='asis'}

cat(unlist(t), sep ="\\clearpage")

```


For the remaining of the analyse, we converted all the data in the same unit (Number of fish to Tons) as it makes it easier to compare the two tRFMOs captures. 

## Converted data

```{r}
list_files_converted <- as.list(list.files(here("outputs/charts/overlapping/IOTC_WCPFC/species_doubled/converted")))


```



```{r results='asis'}

t <- lapply(list_files_converted,resume_knit_child)

```

```{r results='asis'}

cat(unlist(t), sep ="\\clearpage")

```


For this data, WCPFC is almost all the time higher than IOTC data, however the data is initially more in Number of fish than for IOTC. Then it would be better to keep the data from WCPFC, but we should have corresponding conversion factors. 

The only specie for which IOTC have higher records is SWO but it would be to complicated to make a choice for every species. Moreover, the data is not this different for the two tRFMOs, still it has to be noted that it is not homogeneously reported geographically. 







# Annexe

## Unique species

```{r}

list_files_converted <- as.list(list.files(here("outputs/charts/overlapping/IOTC_WCPFC/species_unique")))

```



```{r results='asis'}

t <- lapply(list_files_converted,resume_knit_child)

```

```{r results='asis'}

cat(unlist(t), sep ="\\clearpage")

```



## Plots without conversion

```{r include = FALSE}

list_files <- as.list(list.files(here("outputs/charts/overlapping/IOTC_WCPFC/species_doubled")))
list_charts_double_decla <- list_files[!str_detect(list_files,"converted")]
list_charts_double_decla <- list_files[!str_detect(list_files,"single")]


```



```{r results='asis'}

t <- lapply(list_charts_double_decla,resume_knit_child)

```

```{r results='asis'}

cat(unlist(t), sep ="\\clearpage")

```




